%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Caliz Blanco,\linebreak Alejo Martin Ezequiel}
\address{2922 Domingo de Acassuso \linebreak Olivos Buenos Aires 1636}
\contacts{(+54) 011 32935066 \linebreak alejocalizblanco@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Full Stack Developer}{NDA - Nutrición en Acción}{January 2024 -- Present}
			NDA App
			\begin{itemize}
				\item Developed various features for both nutritionists and patients.
				\item Upgraded part of the infrastructure by replacing outdated technologies with industry-standard solutions.
				\item Implemented a multi-tenant business model by reusing existing code within the app.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Junior Teaching Assistant}{Facultad de Ingeniería, Universidad de Buenos Aires}{August 2022 -- Present}
			Data Science
			\begin{itemize}
				\item Designed and graded various projects focused on data analytics, data manipulation, and machine learning.
				\item Prepared and delivered lectures to classes of over 100 students.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Junior Teaching Assistant}{Facultad de Ingeniería, Universidad de Buenos Aires}{February 2024 -- Present}
			Database Systems
			\begin{itemize}
				\item Designed and graded exams covering topics such as SQL, NoSQL, concurrency in databases, distributed databases, entity-relationship diagrams, relational algebra, and more.
				\item Prepared and delivered lectures to classes of over 100 students.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{CABA, Buenos Aires}{Facultad de Ingeniería, Universidad de Buenos Aires}{July 2018 -- February 2025}
			Software Engineering
			\begin{itemize}
				\item Software architecture, concurrent programming, and distributed systems.
				\item Operating systems, databases, and data structures.
				\item Data science, data analytics, and data engineering.
				\item Algorithms, computer architecture, and software engineering principles.
				\item Programming methodologies and best practices.
				\item Physics, mathematics, and statistics.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}	
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Ahorratón} (2024). A PWA designed to help users save money by comparing prices at different supermarkets. Technologies used: Python, React, MUI, SQL, and Docker.
				\item \textbf{Twitter-like Social App} (2023). A microservices-based social networking application enabling users to post "tweets," upload images, follow other users, and more. Technologies used: Python, Go, JavaScript, React, SQL, NoSQL, Docker, and Kubernetes.
				\item \textbf{Left 4 Dead 2D Clone} (2023). An online multiplayer co-op game supporting multiple simultaneous sessions, built with a client-server architecture. Implemented in C++.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{Proficient in:}
				\subitem Python; SQL; React; Docker; Git; UNIX; NoSQL; Pandas; Spark; Selenium (Web Scraping)
				\item \textbf{Competent in:}
				\subitem Go (Golang); C++; JavaScript; Vue
				\item \textbf{Familiar with and eager to learn:}
				\subitem Rust; C; Ruby; Angular; Flutter; Swift; AWS; Azure; GCP
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	
\end{document}

